---
title: "Final Project"
output: html_notebook
---

## Steps of the data analysis process

### Ask

Three questions to answer:

1.  How do annual and casual riders differ?
2.  Why would a casual rider upgrade to an annual membership?
3.  How can the company use digital media to influence this upgrade?

Case study road map - Ask

Guiding questions

-   What is the problem you are trying to solve?

-   How can your insights drive business decisions?

Key tasks

1.  Identify the business task
2.  Consider key stakeholders

**Deliverable**

-   *A clear statement of the business task*

### Prepare

Guiding questions

-   Are there any problems with the data?

-   How does it help you answer your questions?

Key tasks

1.  Download data and store it
2.  Identify how it's organized.
3.  Sort and filter the data.

Deliverable

-   A description of all the data sources used

### Process

Now, process our data for analysis using the following guidelines

Guiding questions

-   What tools are you choosing and why?

-   Have I verified that the data is clean and ready to analyze?

-   Have I documented the cleaning process so I can share the results?

Key tasks

1.  Check the data for errors.
2.  Choose your tools.
3.  Transform the data so that you can work with it effectively

Deliverable

-   Documentation of any cleaning or manipulation of data

#My Python stuff goes here

###Analyze

```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
getwd()
setwd('./')
```

```{r}
setwd('./data/time_filtered/')
df_2021_08 <- read_csv('202108-divvy-tripdata.csv') 
df_2021_09 <- read_csv('202109-divvy-tripdata.csv') 
df_2021_10 <- read_csv('202110-divvy-tripdata.csv') 
df_2021_11 <- read_csv('202111-divvy-tripdata.csv') 
df_2021_12 <- read_csv('202112-divvy-tripdata.csv') 
df_2022_01 <- read_csv('202201-divvy-tripdata.csv') 
df_2022_02 <- read_csv('202202-divvy-tripdata.csv') 
df_2022_03 <- read_csv('202203-divvy-tripdata.csv') 
df_2022_04 <- read_csv('202204-divvy-tripdata.csv') 
df_2022_05 <- read_csv('202205-divvy-tripdata.csv') 
df_2022_06 <- read_csv('202206-divvy-tripdata.csv') 
df_2022_07 <- read_csv('202207-divvy-tripdata.csv') 
```

### Are all the columns the same throughout the dataframes?

```{r}
print(colnames(df_2021_08) == colnames(df_2021_09))
print(colnames(df_2021_08) == colnames(df_2021_10))
print(colnames(df_2021_08) == colnames(df_2021_11))
print(colnames(df_2021_08) == colnames(df_2021_12))
print(colnames(df_2021_08) == colnames(df_2022_01))
print(colnames(df_2021_08) == colnames(df_2022_02))
print(colnames(df_2021_08) == colnames(df_2022_03))
print(colnames(df_2021_08) == colnames(df_2022_04))
print(colnames(df_2021_08) == colnames(df_2022_05))
print(colnames(df_2021_08) == colnames(df_2022_06))
print(colnames(df_2021_08) == colnames(df_2022_07))
```

### Yes


```{r}
all_trips <- bind_rows(df_2021_08, df_2021_09, 
                       df_2021_10, df_2021_11,
                       df_2021_12, df_2022_01,
                       df_2022_02, df_2022_03,
                       df_2022_04, df_2022_05,
                       df_2022_06, df_2022_07)
```

```{r}
colnames(all_trips)
```

```{r}

```


### Share

### Act

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.
